Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-16 main.tex
Update on Overleaf.

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$,
the \textit{algebraic shape measure} $\kappa_{2}(T)$,
and the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$ 
by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \kappa_{\maxcol}(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \kappa_{2}(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
    ,
    \quad 
    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
    ,
    \quad 
    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
    .
\end{align}
We call these the geometric, algebraic, and aspect shape measure, respectively, of the triangulation.

>>>>

Whenever $T$ is any $n$-dimensional simplex $T$,
we define the \textit{geometric shape measure} $\kappa(T)$,
the \textit{aspect shape measure} $\kappa_{\maxcol}(T)$,
and 
the \textit{algebraic shape measure} $\kappa_{2}(T)$
by 
\begin{align}\label{math:shapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    ,
    \qquad 
    \kappa_{\maxcol}(T)
    := 
    \frac{ \diam(T) }{ \height(T) }
    ,
    \qquad 
    \kappa_{2}(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\min}( \Jacobian \varphi ) }
%     \sup_{ \varphi : \Delta^n \rightarrow T } \| \Jacobian \varphi \|_{\maxcol} \| \Jacobian \varphi^{-1} \|_{\maxcol}
    ,
\end{align}
where the last supremum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$. 
% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.

When $\calT$ is an $n$-dimensional simplicial complex, we naturally introduce 
\begin{align}\label{math:shapemeasure:triangulation}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T)
    ,
    \quad 
    \kappa_{\maxcol}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{\maxcol}(T)
    ,
    \quad 
    \kappa_{2}(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa_{2}(T)
    .
\end{align}
We call these the geometric, aspect, and algebraic shape measure, respectively, of the triangulation.
